QPLIB: A Library of Quadratic Programming Instances

### 2017-02-02 QPLIB.tex
update acknowledgement

We are grateful to all the donors who provided instances for the library. We gratefully acknowledge the financial support of the Gaspard Monge Program for Optimization and operations research (PGMO)  and the logistic support of GAMS for having provided us with the license of their software. Finally, we would like to acknowledge the financial and networking support by the COST Action TD1207.
The fifth author was supported by the Research Campus MODAL \emph{Mathematical Optimization and Data Analysis Laboratories} funded by the Federal Ministry of Education and Research (BMBF Grant~05M14ZAM).  All responsibilty for the content of this publication is assumed by the authors.

>>>>

We are grateful to all the donors who provided instances for the library. We gratefully acknowledge the financial support of the Gaspard Monge Program for Optimization and operations research (PGMO)  and the logistic support of GAMS for having provided us with the license of their software. Finally, we would like to acknowledge the financial and networking support by the COST Action TD1207.
The work of the fifth and twelfth author was supported by the Research Campus MODAL \emph{Mathematical Optimization and Data Analysis Laboratories} funded by the Federal Ministry of Education and Research (BMBF Grant~05M14ZAM).  All responsibilty for the content of this publication is assumed by the authors.
